Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-28 interviews.tex
use block quotes some places

But even correcting notebooks can come too late: ``I'll make a notebook of a
little tutorial of basic functions and what they do, and then I'll send [it]
out, and then people will give me feedback on [it], or have some new feature, or
I'll realize something's wrong, and then I'll go back and change it and update
that page, but then what happens is people have in the meantime forked it. [...]
Usually what it'll be is actually that I'll have to change a package as well, so
their old fork stops working, and then they complain. [...] This probably bites
me more than other people, because I'm doing development so things are changing
as they're looking at the code. Like, iotools, a lot of the functions change
names or change syntax.''

Taylor tried to keep his notebook tree tidy, but this didn't help either, because
notebooks still exist when they have left the tree. ``That's just a problem because people will have old notebooks that
don't work anymore. It's annoying when it's a notebook that I still have and the
format has changed just a bit. More than that is when people have, now that I
know that you can't even delete notebooks, they'll have a fork of something that
doesn't exist anymore on my thing.'' ``Now I'm really gun-shy about sharing
notebooks because it's like, do I want to support this forever?''

Taylor: ``A good example is, someone was complaining about doing forking in an
RCloud notebook. They were trying to use a parallel package. And I said, no no I
think it works, and I did like a one-cell thing that just did some sweep kind of
thing to show that it was actually working in parallel, and then I just deleted
it, thinking it was gone. And then it saved something in a directory that I then
deleted, because it was just a temporary directory. Three months later, I don't
know why they were running it, they said `oh it doesn't work'. I think that's
the biggest issue I'm having right now, all these forks.''

Taylor and Horace work together on a notebook. ``There's no way for both of us
to have ownership of a notebook, so the only way is to fork it back and forth,
and so we have dozens of old copies. [We end up] deleting all the old ones, but
people still have links to them, because they don't actually disappear. [...]
The UI makes it easy to go back to the old stale versions, because you can say
`forked from' `forked from' `forked from', but there's actually no way to go the
way that we want people to go, which is, like, up the tree.''

>>>>

But even correcting notebooks can come too late:
\begin{quote}
I'll make a notebook of a
little tutorial of basic functions and what they do, and then I'll send [it]
out, and then people will give me feedback on [it], or have some new feature, or
I'll realize something's wrong, and then I'll go back and change it and update
that page, but then what happens is people have in the meantime forked it. [...]
Usually what it'll be is actually that I'll have to change a package as well, so
their old fork stops working, and then they complain. [...] This probably bites
me more than other people, because I'm doing development so things are changing
as they're looking at the code. Like, iotools, a lot of the functions change
names or change syntax.
\end{quote}

Taylor tried to keep his notebook tree tidy, but this didn't help either, because
notebooks still exist when they have left the tree.
\begin{quote}
That's just a problem because people will have old notebooks that
don't work anymore. It's annoying when it's a notebook that I still have and the
format has changed just a bit. More than that is when people have, now that I
know that you can't even delete notebooks, they'll have a fork of something that
doesn't exist anymore on my thing [...] Now I'm really gun-shy about sharing
notebooks because it's like, do I want to support this forever?

[...] A good example is, someone was complaining about doing forking in an
RCloud notebook. They were trying to use a parallel package. And I said, no no I
think it works, and I did like a one-cell thing that just did some sweep kind of
thing to show that it was actually working in parallel, and then I just deleted
it, thinking it was gone. And then it saved something in a directory that I then
deleted, because it was just a temporary directory. Three months later, I don't
know why they were running it, they said `oh it doesn't work'. I think that's
the biggest issue I'm having right now, all these forks.
\end{quote}

Taylor and Horace work together on a notebook.

\begin{quote}
There's no way for both of us
to have ownership of a notebook, so the only way is to fork it back and forth,
and so we have dozens of old copies. [We end up] deleting all the old ones, but
people still have links to them, because they don't actually disappear. [...]
The UI makes it easy to go back to the old stale versions, because you can say
`forked from' `forked from' `forked from', but there's actually no way to go the
way that we want people to go, which is, like, up the tree.
\end{quote}
